Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2021-09-15 RR_manuscript/Draft_RR.Rmd
♻️ - mv links to main text; rm individual links

An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).^["Questions" and "Join Project" buttons will be functioning when recruitment starts. "Join Project" will link to the intake form.]
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth. 
Social media advertising will be accompanied by a short recruitment form available at LINK.^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Recruitment form.]
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines. 
All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (LINK^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Analytical approach form.]).
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
Recruitment for this project will commence upon receiving in-principle acceptance.
As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient. Given the exploratory nature of our study, however, we will sample as many analysts as possible. We have received initial expression of interest to participate from more than 200 analysts.

>>>>

An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).^["Questions" and "Join Project" buttons will be functioning when recruitment starts. "Join Project" will link to the intake form.]
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
Recruitment for this project will commence upon receiving in-principle acceptance.
As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient. Given the exploratory nature of our study, however, we will sample as many analysts as possible. We have received initial expression of interest to participate from more than 200 analysts.

### 2021-09-15 RR_manuscript/Draft_RR.tex
♻️ - mv links to main text; rm individual links

The project OSF repository contains all the materials mentioned in this paper and can be accessed at LINK.\footnote{Temporary link: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
The main repository holds two OSF components, \texttt{Data} and \texttt{Questionnaires}, and it is linked to the GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.

All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
Informed consent will be obtained as part of the intake form.

@@

The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).\footnote{A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://osf.io/h6z8w/?view_only=6faaae5feabe4eed800a7c142fcda06f}. The direct link to the intake form questionnaire is \url{https://osf.io/w7db5/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
To do so, they will be given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.\footnote{These can be found in the \texttt{Data} component at \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}

Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.\footnote{Direct link: \url{https://osf.io/ad862/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.

@@

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.\footnote{Direct link: \url{https://osf.io/a3urw/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}, for peer-review: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}).
Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
We will also archive copies of our survey instruments from analysts and peer-reviewers.

>>>>

The project OSF repository contains all the materials mentioned in this paper and can be accessed at \url{https://bit.ly/3AqU1ul}.
The main repository holds three OSF components, \texttt{Data}, \texttt{Questionnaires}, and \texttt{Cache}, and it is linked to the GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
Informed consent will be obtained as part of the intake form.

@@

The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://bit.ly/3Cf3fdm}.
The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
To do so, they will be given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
These can be found in the \texttt{Data} component at \url{https://bit.ly/3Ahawc7}.

Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.

@@

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}, link for peer-review: \url{https://bit.ly/3AqU1ul}).
Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
We will also archive copies of our survey instruments from analysts and peer-reviewers.
